### 2024-01-11 ms.qmd
Updates

### Statistical analyses

## Results

# References

>>>>

### Statistical analyses
- We split by species to analyse them separately. We also saw a significant effect of the colour assigned (blue or red) in the preliminary analises, so we decided to split the data by colour as well.

### Results
```{r, cleaning}
#| label: cleaning
source(here("R", "1_data_process.R"))
# Once we run this code, the result will be two different dataframes, one for the Associative learning task (data_asso) and the other for the Reversal learning task (data_rev).
write.csv(data_asso, file= "./output/databases_clean/data_asso.csv")
write.csv(data_rev, file= "./output/databases_clean/data_rev.csv")
```

```{r, models}
#| label: models
# fitting the model and extraction of posteriors for both types of task and species using fit_m function
source(here("R", "func.R"))
# A) Associative task. Model formula: FC_associative ~ Associative_Trial*cort*temp + (1 + Associative_Trial|lizard_id)
## A.1) L. delicata
deli_asso_red <- fit_m("asso", "deli", "red")
write.csv(deli_asso_red, file= "./output/Checking/deli_asso_red.csv")
deli_asso_blue <- fit_m("asso", "deli", "blue")
write.csv(deli_asso_blue, file= "./output/Checking/deli_asso_blue.csv")
## A.2) L. guichenoti
guich_asso_red <- fit_m("asso", "guich", "red")
write.csv(guich_asso_red, file= "./output/Checking/guich_asso_red.csv")
guich_asso_blue <- fit_m("asso", "guich", "blue")
write.csv(guich_asso_blue, file= "./output/Checking/guich_asso_blue.csv")
# B) Reversal task. Model formula: FC_reversal ~ trial_reversal*cort*temp + (1 + trial_reversal|lizard_id)
## B.1) L. delicata
deli_rev_red <- fit_m("rev", "deli", "red")
write.csv(deli_rev_red, file= "./output/Checking/deli_rev_red.csv")
deli_rev_blue <- fit_m("rev", "deli", "blue")
write.csv(deli_rev_blue, file= "./output/Checking/deli_rev_blue.csv")
## B.2) L. guichenoti
guich_rev_red <- fit_m("rev", "guich", "red")
write.csv(guich_rev_red, file= "./output/Checking/guich_rev_red.csv")
guich_rev_blue <- fit_m("rev", "guich", "blue")
write.csv(guich_rev_blue, file= "./output/Checking/guich_rev_blue.csv")
```

```{r, resultsAssodeli}

```

```{r, results}
```

```{r, plots}
```

## References
